A large leading tail of atmospheric escape in the HAT-P-67 b system

### 2023-03-14 paper/paper1/ms.tex
Text describing the MCMC fitting, probably too verbose

>>>>

% We will probably delete all of this in favor of fitting just the static-subtracted strategy, and merely stating the Si internal precision.
We estimated bulk characteristics of the spectral line by fitting a pair of Voigt profiles to the 10828$-$10838 \AA region.  The blue Voigt profile was intended to fit the Si line centered at 10830 \AA, acting as static control sample.  The red line initialized at 10833 \AA was intended to aglomerate all three components of the metastable triplet into a single feature, consistent with their appearance in Figure \ref{fig:HPFheliumOverview}.  The model constructed in this way has a total of 8 parameters: amplitude $A$, location $\lambda_c$, Gaussian width $\sigma$, and Lorentzian width $\gamma$ for each of the two pseudo-lines.  This phenomenological choice was intended not to match the underlying substructure of the line, but instead merely to match the bulk characteristics in the region of interest.  The choice of Voigt profiles---as opposed to simple Gaussians---provides enough model flexibility to make up for possible deficiencies in the continuum assignment and line shapes.

The individual fits to the Si line show a line center position of typically $X\pm z$.  The weighted mean of all 152 spectra shows a mean of $Y\pm w$.  In contrast, the Helium 10833 bulk feature shows a phase-dependent velocity shift.  The out-of-transit phases exhibit \censor{XX}, consistent with the stellar \ion{He}{1} rest frame zero velocity.  The extended ingress and in-transit phases exhibit a blueshift of \censor{xpmz}.

The model constructed in this way smears the apparent shift, since the static underlying stellar spectrum tends to dilute the dynamic portion of the line.  So we repeated the line fitting by subtracting off a model of the out-of-transit stellar spectrum.  While any interpolation strategy would work, we chose to a Gaussian Process GP model \censor{cite DFM}.  This GP strategy has the advantage of providing principled uncertainty bands, useful for quantifying our confidence in putative weak signals in the presence of correlations.
